An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-07 gas-adsorption/referee-response.md

Dear editor,

The responses of referees 1 and 3 could hardly be more divergent.  Our work is impactful precisely because it can tell researchers when to stop looking... or perhaps more relevantly it can tell funding agencies when to stop funding research in this direction.  This is threatening, and Referee 1 doesn't seem interested in knowing whether we should stop looking at porous materials for natural gas and hydrogen storage.

# Referee 1

Referee 1 states that "Phenomenological predictions without any relation to real
materials are not very helpful, if not useless."  The referee fails to grasp
that our theory *does* take into account the gas, and places a fundamental limit
on the capacity of an entire class of materials (inflexible porous materials).
This is far from useless.  The referee suggests as superior an approach
involving screening hundreds of thousands of actual or theoretical MOFs.

    Such a study is indeed valuable for guiding the development of improved MOFs,
    but is entirely unable to place a rigorous upper bound on the attainable
    capacity, since it is always possible that there is a better structure out
    there. We have edited the paragraph on page 3 of the paper that discusses
    this sort of study to make this more clear (and added a reference the paper
    by Ahmed et al.).

### 2021-07-07 gas-adsorption/rsc-gas-ads-complete.tex
more edits

Finally, empirical models that statistically relate e.g., surface area to 
hydrogen adsorption \cite{firlej2013understanding,goldsmith2013theoretical}
have been used to determine what properties a material must possess to reach
a given storage target.

>>>>

\startreferees{Added discussion of screening studies}
Finally, a number of empirical studies have been performed that computationally
simulate a adsorption in a vast array of possible porous
structures~\cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional}.  Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  However, such an approach can only place a \emph{lower
bound} on the highest attainable deliverable capacity.
